The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-03-18 paper/ms.tex
removed relative velocity subsection

We estimate the expected distribution of displacements between the two
dominant dark matter density peaks and between baryons and dark matter
in halos simulated within a full cosmological context. We use as a benchmark the
observation of \bullg, which is the lowest mass system observed so far
featuring a bi-modal dark matter distribution with a dislocated 
baryonic component. We extend previous results by
studying two halo samples: groups and clusters. We find that $(55\pm 5)\%$
of the dark matter halos with circular velocities in the range
$300\kms$ to $700\kms$ (groups) show multimodal morphologies with
displacements between the dark matter clumps equal or larger than
$133\pm21$\hkpc as observed in \bullg. For dark matter halos with
circular velocities larger than $700\kms$ (clusters) this fraction
rises to $(82\pm 3)\%$. Using the same simulation we estimate the
dark matter-to-baryon spatial separation and find that $0.1$ to
$1.0\%$ of the groups should present separations equal or
larger than $87\pm 14$\hkpc corresponding to our observational
benchmark; for clusters this fraction rises to $(7\pm 3)\%$, consistent
with previous studies of dark matter to baryon separations. The
extension of the theoretical predictions and observational results
towards low mass bi-modal dark matter configurations opens up the
possibility for a new statistical test of  $\Lambda$CDM.
\end{abstract}

@@

%In order to gain better insight, we use two
%quantities that can be infered from the simulation. The first one is
%the sub-structure velocity as a fraction of the host's circular
%velocity, $||\vec{v}||/V_{\rm c, host}$, as a measure of the the
%strength of the merger.  The second onw is $\mu$, which measures the geometry
%(head-on vs. grazing) of each interaction.

@@

%\subsection{Relative Velocities}
%\label{sec:velocities}

%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figure_3.eps}
%\end{center}
%\caption{Integrated probability distribution for the relative velocity of the
%sub-halo with respect to its host. The left panel shows the results
%in physical units while the right panel show the same values
%normalized by the circular velocity of the host halo. The line encoding
%follows the same structure as Figure \ref{fig:displacement}}
%\label{fig:velocities}
%\end{figure*}

@@

Recently \citep{Foex2013} presented an analysis of $80$ galaxy groups
from the SL2S sample. From the light distribution, only $34$ objects
($\approx 42\%$) have regular isophotes, $33$ had ellongated
isophotes (hints of merging system), and $13$ ($\approx 16\%$) had a
clear bi-modal light distribution.

>>>>

We estimate the expected distribution of displacements between the two
dominant dark matter density peaks and between baryons and dark matter
in halos simulated within a full cosmological context. We use as a benchmark the
observation of \bullg, which is the lowest mass system observed so far
featuring a bi-modal dark matter distribution with a dislocated 
baryonic component. We extend previous results by
studying two halo samples: groups and clusters. We find that $(55\pm 5)\%$
of the dark matter halos with circular velocities in the range
$300\kms$ to $700\kms$ (groups) show multimodal morphologies with
displacements between the dark matter clumps equal or larger than
$133\pm21$\hkpc as observed in \bullg. For dark matter halos with
circular velocities larger than $700\kms$ (clusters) this fraction
rises to $(82\pm 3)\%$. Using the same simulation we estimate the
dark matter-to-baryon spatial separation and find that $0.1$ to
$1.0\%$ of the groups should present separations equal or
larger than $87\pm 14$\hkpc corresponding to our observational
benchmark; for clusters this fraction rises to $(7\pm 3)\%$, consistent
with previous studies of dark matter to baryon separations. The
extension of the theoretical predictions and observational results
towards low mass bi-modal dark matter configurations opens up the
possibility for a new statistical test of  $\Lambda$CDM.

NOTA: tomar $186\pm30$ para el DM-DM displacement.

\end{abstract}

@@

@@

@@

Recently \citep{Foex2013} presented an analysis of $80$ galaxy groups
from the SL2S sample. From the light distribution, only $34$ objects
($\sim 42\%$) have regular isophotes, $33$ had ellongated
isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
clear bi-modal light distribution.
